Reconstructing the last known movements of one of Nature's giants

### 2019-01-17 manuscript/PeerJ/blue-new.tex
Add GitHub ref

@@

\subsection{Data Code and Materials}\label{data-code-and-materials}
Data are available from the NHM Data Portal (https://doi.org/10.5519/0093278). 
R code is available from GitHub (https://github.com/nhcooper123/blue-whale-bes)(Zenodo DOI will be added before publication).

>>>>

R code for all analyses is available from GitHub (https://github.com/nhcooper123/blue-whale-bes; \cite{github})

@@

\subsection{Data Code and Materials}\label{data-code-and-materials}
Data are available from the NHM Data Portal (https://doi.org/10.5519/0093278). 
R code is available from GitHub (https://github.com/nhcooper123/blue-whale-bes)(Zenodo DOI 10.5281/zenodo.2542777).
